Numerical experiment investigating the influence of drag on trajectory patterns of floating macroalgae

### 2021-05-11 thesis_chapter_3.Rmd
file rename. updates to chp3. vector map updated

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=12, fig.width=7, fig.cap="Figure 3: Comparison of mean trajectories. Simulations of hydrodynamic drag are presented in Panels A, C, E, G for January, April, July, and October, respectively. Results of simulations including both hydrodynamic drag and wind are in Panels B, D, F, H for January, April, July, and October, respectively."}

@@

```{r shape data outputs, warning=FALSE, echo=FALSE, message=FALSE, fig.cap="Figure 11: Comparison of trajectory data between sphere and cylinder shape coefficients for scenarios 61-64. Row A represents the mean trajectory comparison for each of the respective months (seasons) simulated. The reader is referred to tables 1 and 2 for details pertaining to each scenario.", fig.height=8, fig.width=6}

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=10, fig.width=8, fig.cap="Figure 3: Comparison of mean trajectories. Simulations of hydrodynamic drag are presented in Panels A, C, E, G for January, April, July, and October, respectively. Results of simulations including both hydrodynamic drag and wind are in Panels B, D, F, H for January, April, July, and October, respectively."}

@@

```{r shape data outputs, warning=FALSE, echo=FALSE, message=FALSE, fig.cap="Figure 11: Comparison of trajectory data between sphere and cylinder shape coefficients for scenarios 61-64. Row A represents the mean trajectory comparison, row B-C are density comparison plots, and row D is comparison of total distance travelled from the release site for each of the respective months (seasons) simulated.  The reader is referred to tables 1 and 2 for details pertaining to each scenario.", fig.height=8, fig.width=6}
